%%%%%%%%%%%%%%%%%
% \documentclass[10pt,a4paper,academicons]{altacv}

% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e]{altacv}

% Change the page layout if you need to
\geometry{left=2cm,right=10cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}

\ifxetexorluatex
 
  \setmainfont{Carlito}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{\fontsize{18}{20}\selectfont Dhruv Gupta}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{\href{https://mail.google.com/mail/u/0/#inbox}{b21008@students.iitmandi.ac.in}}
  \phone{+91 9646463838}
  \location{Chandigarh}
  \linkedin{\href{https://www.linkedin.com/in/dhruv-gupta-956279228/}{linkedin.com/in/dhruv-gupta-956279228}}
   \github{\href{https://github.com/dhruvik3610}{github.com/dhruvik3610}}
}

\begin{fullwidth}
\makecvheader


\AtBeginEnvironment{itemize}{\small}

\cvsection{\fontsize{14}{16}\selectfont Education}

%\divider
\cvevent{\fontsize{11}{13}\selectfont \bf B. Tech. BioEngineering, Minor in Intelligent Systems | Indian Institute of Technology, Mandi}{}{ Nov 2021 -- Present (Till June 2025)}{}
\begin{itemize}
\item Relevant Courses - Data Science- 1,2,3 (Python,Probability \&
Machine Learning), Data Handling and Visualization, Deep Learning and its Applications, Biostatistics, Linear Algebra, Bioinformatics, Signals and Systems
\item CGPA: {\bf 7.93} (upto sixth semester)
\end{itemize}

%\divider

\cvsection{\fontsize{14}{16}\selectfont TECHNICAL SKILLS}
\begin{itemize}

\item {\bf Languages: }[Python, SQL, MySQL](Most experience), [R, HTML-CSS](Intermediate level Experience), [C++, Perl](Beginner Level  experience)
\item {\bf Frameworks and Relevant Libraries: }Tensorflow, Keras, ScikitLearn, Pandas, Numpy, Matplotlib
\item {\bf IDEs and Programming Tools: } Spyder, Visual Studio Code, Jupyter Notebook, Google Colab
\item {\bf MOOCs:} SQL for data analysis
\end{itemize}

\cvsection{\fontsize{14}{16}\selectfont Experience}

\cvevent{\fontsize{11}{13}\selectfont \bf Data Science Intern | Brainwave Science, Boston, USA}{}{ \fontsize{8}{10}\selectfont March 2024 -- May 2024}{}
%\begin{tabular}{rl}
%\textbf{Duration:} & January 2024 - June 2024 (6 months) \\
%\textbf{Location:} & Remote [Boston, ]
%\end{tabular}

\begin{itemize}
%\item Collaborated with cross-functional teams to develop and implement innovative solutions for clients, leveraging expertise in [specific skills or areas of expertise].
\item Developed and implemented data analysis pipelines using MNE-Python for processing and analyzing EEG/MEG data to enhance the functioning of brainwave detecting headset, {\bf iCognative}.
\item Conducted preprocessing tasks including filtering, artifact correction, and epoching using {\bf regression} and {\bf independent component analysis} to prepare EEG/MEG data for advanced analysis.
\item Skills - {\bf Machine Learning}, {\bf MNE Python}, {\bf Data Analysis}
\end{itemize}

\cvsection{\fontsize{14}{16}\selectfont ProjectS}
\cvproject{VineNet - Real-Time Grape Bunch Segmentation[\href{https://github.com/dhruvik3610/VineNet---Grape-Bunch-Segmentation}{Github Link}] \hfill  \textnormal{(Machine Learning Project)}} 
\begin{itemize}
 \item Developed an optimized U-Net model for precise semantic segmentation of grape bunches in high-resolution vineyard images, achieving a Training IoU of 0.96 and Validation IoU of 0.71.
 \item Conducted extensive training over 250 epochs on a high-resolution, labeled dataset, specifically curated to enhance model precision in vineyard applications.
\end{itemize}
\smallskip
\smallskip
%\smallskip
%\cvproject{AI for Agriculture: Grape Bunch Segmentation Expert[\href{https://drive.google.com/file/d/1BrCJO5i4h4SJmLRL3lleFWggeXDFA_Fb/view?usp=sharing}{Report Link}]  (Python, OpenCV)\hfill \textnormal{(Computer Vision)} }
%\begin{itemize}
 %\item Designed and implemented a real-time driver drowsiness detection system using computer vision and machine learning (Support Vector Machine, Histogram of Oriented Gradients, etc.).  
 %\item Leveraging facial landmarks and eye aspect ratio (EAR) to monitor and alert for signs of driver fatigue, enhancing road safety.
%\end{itemize}
%\smallskip

%\smallskip


\cvproject{Resume Parser[\href{https://github.com/dhruvik3610/Resume-Parser-and-Matcher}{Github Link}]  (Python, NLP, Spacy3, Custom NER)\hfill \textnormal{(Machine Learning Project)} }
\begin{itemize}
 \item Developed and implemented an efficient resume parser using natural language processing (NLP) techniques to extract key information optimizing
the recruitment process.
 \item Utilized machine learning algorithms to give score to an input resume by extracting particular keywords from that resume and comparing them with the keywords with an accuracy of 87\%.
\end{itemize}

\cvsection{\fontsize{14}{16}\selectfont Awards \& Achievements}

\begin{itemize}


\item Won {\bf 2nd prize} in {\bf AI Innovation} hackathon conducted by Yahama in collaboration with IIT Mandi.
\item {\bf Completed SQL 50 Challenge on LeetCode}: Demonstrated advanced SQL proficiency by solving 50 SQL-focused problems on LeetCode.
\item {\href{https://github.com/dhruvik3610/JPMC_certificate}{JPMC Virtual Internship} } - Participated in JPMorgan Chase Co. Virtual Internship Program, gaining practical experience in the financial industry and utilized various algorithms in Python, React, Typescript and Git. Also used JPMC's tool - "Perspective", to visualise data on web applications.

\end{itemize}


\cvsection{\fontsize{14}{16}\selectfont Positions of Responsibility}

\begin{itemize}

\item {\bf UnderGraduate Academic Council}- Branch Councillor for BioEngineering branch at UGAC, IIT Mandi.
\item {\bf Event Coordinator, Exodia}- Successfully coordinated Quiz event in Exodia, The Annual Cultural Fest of IIT Mandi.
\item {\bf Quriosity}- Core Team Member at Quriosity, The Quizzing club of IIT Mandi.
\item {\bf Session organizer, UGAC} - Conducted a guidance session for junior students, providing insights and advice to support their academic and career development.

\end{itemize}







\end{fullwidth}
\end{document}
